README

### 2023-08-07 README.Rmd
modified readme

-   .Rprofile - defines paths and activates `renv`, options for Posit R package manager
-   manuscript - manuscript, bibliography, cover letter and meta files to render to .docx format
-   tables - main and supplementary tables (R objects and .docx format)
-   figures - main and supplementary figures (R objects and .docx format)
-   renv/renv.lock - `renv` directories to manage R dependencies and versions used in this simulation

>>>>

-   manuscript - manuscript, bibliography, cover letter and meta files to render to .docx format
-   tables - main and supplementary tables (R objects and .docx format)
-   figures - main and supplementary figures (R objects and .docx format)
-   renv/renv.lock - `renv` directories to manage R dependencies and versions used in this simulation
-   .Rprofile - defines paths and activates `renv`, options for Posit R package manager
